SPIDERMAN: an open source code to model phase curves and secondary eclipses.

### 2016-10-24 ms.tex
hello

Using an analytical approximation to the results of General Circulation Models, we apply the code to archival data on the phase curve of WASP-43b, providing an excellent fit to the data, and placing constraints of the physics of the atmosphere, such as the ratio between advective and radiative timescales.

@@

There are a small number of different general "cases" for the numbers of triangles and segments that must be used, that can be selected based on the number and types of "collision points" between the planet region and the stellar circle. Therefore, the first step for calculating the occulted area for each segment of the planet is to calculate these collision points. Within \textsc{spiderman} the region boandaries are stored as the radius of the inner and outer arcs, and the $\theta$ angle of the two radial lines.

Finding the collision points between an arc or a line and a circle (the star), if any exist, are trivial and fast to calculate. The code then classifies the geometric "case" of the collision based on the number of collision points on the 4 boundary sides.

@@

The $\xi$ parameter is perhaps the most interesting, as it effectively parameterises the degree to which the hotspot of the planet will be offset from the substellar point by the circulation of the plant's atmosphere. The effects of this can be seen in \ref{fig:ex_lcs}, where

@@

The systematics have effects on scales of \emph{visits}, \emph{orbits} and individual exposures, where a visit is a continuous set of orbits directed at a target. Due to the low earth orbit of Hubble, each complete orbit lasts 95 minutes, and for approximately half of this time the target will be unobservable due to being behind the Earth. For this reason, a complete exoplanet transit can not be observed with one "visit", and it is necessary to observe several transits with different temporal phasing to completely cover the full orbital phase of the system.

@@

The majority of this work was carried out at the kavli summer program in physics 2016. T.L extends his gratitude to the program organisers, in particular Jonothan Fortney and Pascale Garaud.

>>>>

Using an analytical approximation to the results of General Circulation Models, we apply the code to archival data on the phase curve of WASP-43b, providing an excellent fit to the data, and placing constraints on the physics of heat transport in the atmosphere, such as the ratio between advective and radiative timescales.

@@

There are a small number of different general ``cases" for the numbers of triangles and segments that must be used, that can be selected based on the number and types of ``collision points" between the planet region and the stellar circle. Therefore, the first step for calculating the occulted area for each segment of the planet is to calculate these collision points. Within \textsc{spiderman} the region boandaries are stored as the radius of the inner and outer arcs, and the $\theta$ angle of the two radial lines.

Finding the collision points between an arc or a line and a circle (the star), if any exist, are trivial and fast to calculate. The code then classifies the geometric ``case" of the collision based on the number of collision points on the 4 boundary sides.

@@

The $\xi$ parameter is perhaps the most interesting, as it effectively parameterises the degree to which the hotspot of the planet will be offset from the substellar point by the circulation of the plant's atmosphere. The effects of this can be seen in \ref{fig:ex_lcs}, where both the position of the maxima of the phase curve, and the shape of the ingress and egress of the secondary eclipse are clearly effected by this asymmetry.

@@

The systematics have effects on scales of \emph{visits}, \emph{orbits} and individual exposures, where a visit is a continuous set of orbits directed at a target. Due to the low earth orbit of Hubble, each complete orbit lasts 95 minutes, and for approximately half of this time the target will be unobservable due to being behind the Earth. For this reason, a complete exoplanet transit can not be observed with one ``visit", and it is necessary to observe several transits with different temporal phasing to completely cover the full orbital phase of the system.

@@

The majority of this work was carried out at the kavli summer program in physics 2016. T.L extends his gratitude to the program organisers, in particular Jonathan Fortney and Pascale Garaud.
